A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-04-30 manuscript.Rmd
restructure the archiving section #15

# Creating a public release

>>>>

# Archive Milestones

The open nature of the here proposed workflow does blur the lines between published and unpublished.
However, even when your Git repository is public, you may want to signify important stages of your project, like preregistration, preprint, submission and acceptance to the journal.
These milestones deserve to be archived.
A project is only then properly archived when it is stored at least at two independent storage locations and reproducible from all locations.
Therefore, you should make extra sure that the project at these points is reproducible.
Ideally, you ask a coworker or collaborator to reproduce the project independently from you.
The sections [Creating a DOI] and [Creating a Release] describe how you can easily create three different openly accessible longterm archived copies of your project.

## Creating a DOI

## Creating a Release

GitHub has a "release" function, which creates a link to a specific version of your project, where everything is available as a zip file.
You have the opportunity to describe the release in the release notes and to upload other additional files (e.g. the rendered pdf).

## Archiving Docker

## Archiving Data
